# Reproducible Research: Peer Assessment 1

## Loading and preprocessing the data
```{r loaddata}
        setwd("c:/r/knitr//RepData_PeerAssessment1")
        data<-read.csv(file = "activity.csv")
```



## What is mean total number of steps taken per day?

```{r}
        # For this Assignment consider only those observations 
        # for which all data is present
        completed <-data[complete.cases(data),]

        # Create new data frame with list of dates and sum, 
        # mean and median of steps taken for that particular day
        library(plyr)
        dailysteps<-ddply(completed,.(date),summarize,sum=sum(steps), 
                          mean=mean(steps), median=median(steps))

        hist(dailysteps$sum,xlab = "Total Steps", 
             main="Total Steps Taken Each Day", col = "red", breaks=20 )

        
        dailysteps[,c("date", "mean","median")]


```

## What is the average daily activity pattern?

```{r}
        intervaldata<-ddply(completed,.(interval),summarize,sum=sum(steps), 
                            mean=mean(steps), median=median(steps))
        plot(intervaldata$interval, intervaldata$mean, type="l", col="blue", 
             xlab="5 mins Interval ID", ylab="Average number of steps")

        mostactiveinterval<-intervaldata[which.max(intervaldata$mean),"interval"]
```

On average Interval ID = `r mostactiveinterval` contains the maximum number of steps

## Imputing missing values

```{r}
        incompleterecords<-nrow(data)-nrow(completed)

```

Total number of missing records = `r incompleterecords`

## Are there differences in activity patterns between weekdays and weekends?
