# Reproducible Research: Peer Assessment 1

## Loading and preprocessing the data
```{r loaddata}
        setwd("c:/r/knitr//RepData_PeerAssessment1")
        data<-read.csv(file = "activity.csv")
```



## What is mean total number of steps taken per day?

```{r}
        # For this Assignment consider only those observations 
        # for which all data is present
        completed <-data[complete.cases(data),]

        # Create new data frame with list of dates and sum, 
        # mean and median of steps taken for that particular day
        library(plyr)
        dailysteps<-ddply(completed,.(date),summarize,sum=sum(steps), 
                          mean=mean(steps), median=median(steps))

        hist(dailysteps$sum,xlab = "Total Steps", 
             main="Total Steps Taken Each Day", col = "red", breaks=20 )

        
        dailysteps[,c("date", "mean","median")]


```

## What is the average daily activity pattern?

```{r}
        intervaldata<-ddply(completed,.(interval),summarize,sum=sum(steps), 
                            mean=mean(steps), median=median(steps))
        plot(intervaldata$interval, intervaldata$mean, type="l", col="blue", 
             xlab="5 mins Interval ID", ylab="Average number of steps")

        mostactiveinterval<-intervaldata[which.max(intervaldata$mean),"interval"]
```

On average Interval ID = `r mostactiveinterval` contains the maximum number of steps

## Imputing missing values

```{r}
        # Find number of incomplete records
        incompleterecords<-nrow(data)-nrow(completed)
```

Total number of missing records = `r incompleterecords`

```{r}
        # Set default value for number of steps where value is NA
        # Use mean value from Interval Data
        for (i in 1:nrow(data)) {
                row<-data[i,]
                count<-0
                if(is.na(row$steps)) {
                        
                        data[i,"steps"] <-intervaldata[intervaldata$interval==row$interval, "mean"]
                }
        }

        dailysteps<-ddply(data,.(date),summarize,sum=sum(steps), 
                          mean=mean(steps), median=median(steps))

        hist(dailysteps$sum,xlab = "Total Steps", 
             main="Total Steps Taken Each Day", col = "red", breaks=20 )

        
        dailysteps[,c("date", "mean","median")]

```

Values and Charts diifer when compared with data with completed cases and data with NA replaced with mean values for specific 5 min Interval.

Frequency of Total number of steps was highest was increased after setting missing data
## Are there differences in activity patterns between weekdays and weekends?
